MLH1 Data Report

### 2019-08-16 doc/Main_Report.rmd
trying to update report
small work from home

ff
ss
```

@@

```{r age.hists, echo=FALSE}
#meta.data.file2 = read.csv("~./MLH1repo/data/MouseMetaData61119.csv", header = TRUE)
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)
meta.data.file2 <- meta.data.file2[!(is.na(meta.data.file2$mouse)|meta.data.file2$mouse==""),] #375

@@

@@

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
high_qual_boxplot
#not sure why order got messed up again...
```

>>>>

#these plot currently look bad

@@

```{r age.hists, echo=FALSE}

#meta.data.file2 = read.csv("~./MLH1repo/data/MouseMetaData61119.csv", header = TRUE)
meta.data.file2 = read.csv("~./MLH1repo/data/Mouse_MetaData_6.12.19.csv", header = TRUE)
meta.data.file2 <- meta.data.file2[!(is.na(meta.data.file2$mouse)|meta.data.file2$mouse==""),] #375

@@

#add euth date for calculating age
source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
PWD.KAZ_MLH1.imprv <- add_euth_date(PWD.KAZ_MLH1.imprv)
PWD.KAZ_MLH1.imprv <- add_age(PWD.KAZ_MLH1.imprv)

@@

```{r,  show boxplots, fig.height=5, fig.width=8, echo=FALSE}
#high_qual_boxplot
#not sure why order got messed up again...
```
